---
title: "Azimuth Mapping"
output: html_document
date: '2022-11-11'
---

In order to use the Azimuth app through the internet the Seurat object has to be in the format of h5ad file. Do not have to separate out the time points into separate Seurat objects but code is included for reference. 

```{r}
#How to have files be in the proper format so they can be uploaded into Azimuth app

library(Seurat)
library(Azimuth)
library(SeuratData)
library(patchwork)
library(SeuratDisk)

d00_object <- subset(seurat_object_subset, subset = condition == 'CMO301')
d0_object <- subset(seurat_object_subset, subset = condition == 'CMO308')
d7m_object <- subset(seurat_object_subset, subset = condition == 'CMO309')
d14m_object <- subset(seurat_object_subset, subset = condition == 'CMO310')
d14c_object <- subset(seurat_object_subset, subset = condition == 'CMO312')
d7c_object <- subset(seurat_object_subset, subset = condition == 'CMO311')

#Convert each Seurat object into the .h5ad format
SaveH5Seurat(seurat_revised, filename = "seurat_revised.h5Seurat")
Convert("seurat_revised.h5Seurat", dest = "h5ad")

SaveH5Seurat(seurat_object_subset, filename = "seurat_object_subset.h5Seurat")
Convert("seurat_object_subset.h5Seurat", dest = "h5ad")

SaveH5Seurat(seurat_chondro, filename = "seurat_chondro_azimuth_f.h5Seurat")
Convert("seurat_chondro_azimuth_f.h5Seurat", dest = "h5ad")

```

Workflow for inputting azimuth table for human fetal cells. The outputted heatmap is representing the number of cells assigned to a given cell type. 
```{r}
#FETAL W/ ALL DATA

#Uploading data from fetal reference
fetal_all<- read.csv(file = "/project2/gilad/emaan/time_project/data/fetal_all_chondro.tsv", head=TRUE, sep="\t")

#Uploading Seurat object subset original
load("/project2/gilad/emaan/time_project/data/seurat_object_subset.RData")

#Making a table from the Seruat object including only the meta data
seurat_table <- seurat_chondro@meta.data

#In the seurat table making the CMO sequence a column instead of a row
library(tibble)
seurat_table <- tibble::rownames_to_column(seurat_table, "cell")

fetal_all <- merge(seurat_table, fetal_all, by='cell', all.x=TRUE)

#Remove all rows with NA
fetal_all <- fetal_all[complete.cases(fetal_all), ]

#Putting columns in a specific order
fetal_all$condition <- factor(fetal_all$condition, levels = c("D00", "D0", "D7c","D14c"))

#Making heatmap with filling by mapping score
library(ggplot2)
ggplot(data =  fetal_all, aes(x = condition, y = predicted.annotation.l1)) + 
  geom_tile(aes(fill = mapping.score)) + scale_fill_gradient2(high="blue", guide="colorbar",aesthetics="fill") 

```

Workflow for creating a heatmap that has the frequency of cell in a given condition for a given cell type in the human fetal referance. 
```{r}
#FETAL W/ ALL DATA FREQUENCY

#Subseting the fetal all dataframe into dataframes for each time point so we can find the frequencies for cells within each time point

library(dplyr)

# Function to calculate frequency and percentage for a given condition
calculate_frequency <- function(condition, data) {
  subset_data <- subset(data, data$condition == condition, select = c("predicted.annotation.l1","condition"))
  frequency <- count(subset_data, subset_data$predicted.annotation.l1)
  total_samples <- sum(frequency$n)
  frequency$percentage <- (frequency$n/total_samples) * 100
  colnames(frequency)[1] <- "predicted.annotation.l1"
  frequency$condition <- condition
  return(frequency)
}

# Apply the function to each condition
d00_fetal_frequency <- calculate_frequency("D00", fetal_all)
d0_fetal_frequency <- calculate_frequency("D0", fetal_all)
d7c_fetal_frequency <- calculate_frequency("D7c", fetal_all)
d14c_fetal_frequency <- calculate_frequency("D14c", fetal_all)
d7m_fetal_frequency <- calculate_frequency("D7m", fetal_all)
d14m_fetal_frequency <- calculate_frequency("D14m", fetal_all)

# Combine all frequency tables
total_fetal_freq <- rbind(d00_fetal_frequency, d0_fetal_frequency, d7c_fetal_frequency, d14c_fetal_frequency, d7m_fetal_frequency, d14m_fetal_frequency)

# Order the levels of the condition column
total_fetal_freq$condition <- factor(total_fetal_freq$condition, levels = c("D00", "D0", "D7m", "D14m", "D7c", "D14c"))

# Create the plot
ggplot(data = total_fetal_freq, aes(x = condition, y = predicted.annotation.l1)) + 
  geom_tile(aes(fill = percentage)) + 
  scale_fill_gradient2(high = "blue", guide = "colorbar", aesthetics = "fill")

ggplot(data =  total_fetal_freq, aes(x = condition, y = predicted.annotation.l1)) + 
  geom_tile(aes(fill = percentage)) + scale_fill_gradient2(high="blue", guide="colorbar",aesthetics="fill") 

#***D00***
d00_fetal_all <- subset(fetal_all, fetal_all$condition == "D00", select = c("predicted.annotation.l1","condition"))
d00_fetal_frequency <- count(d00_fetal_all, d00_fetal_all$predicted.annotation.l1)
sum(d00_fetal_frequency$n)
d00_fetal_frequency$percentage <- (d00_fetal_frequency$n/sum(d00_fetal_frequency$n)) *100

#***D0***
d0_fetal_all <- subset(fetal_all, fetal_all$condition == "D0", select = c("predicted.annotation.l1","condition")) 
d0_fetal_frequency <- count(d0_fetal_all, d0_fetal_all$predicted.annotation.l1)
sum(d0_fetal_frequency$n)
d0_fetal_frequency$percentage <- ""
d0_fetal_frequency$percentage <- (d0_fetal_frequency$n/sum(d0_fetal_frequency$n)) *100

#***D7C***
d7c_fetal_all <- subset(fetal_all, fetal_all$condition == "D7c", select = c("predicted.annotation.l1","condition"))
d7c_fetal_frequency <- count(d7c_fetal_all, d7c_fetal_all$predicted.annotation.l1)
sum(d7c_fetal_frequency$n)
d7c_fetal_frequency$percentage <- ""
d7c_fetal_frequency$percentage <- (d7c_fetal_frequency$n/sum(d7c_fetal_frequency$n)) *100

#***D14C***
d14c_fetal_all <- subset(fetal_all, fetal_all$condition == "D14c", select = c("predicted.annotation.l1","condition"))
d14c_fetal_frequency <- count(d14c_fetal_all, d14c_fetal_all$predicted.annotation.l1)
sum(d14c_fetal_frequency$n)
d14c_fetal_frequency$percentage <- ""
d14c_fetal_frequency$percentage <- (d14c_fetal_frequency$n/sum(d14c_fetal_frequency$n)) *100

#***D7M***
d7m_fetal_all <- subset(fetal_all, fetal_all$condition == "D7m", select = c("predicted.annotation.l1","condition"))
d7m_fetal_frequency <- count(d7m_fetal_all, d7m_fetal_all$predicted.annotation.l1)
sum(d7m_fetal_frequency$n)
d7m_fetal_frequency$percentage <- ""
d7m_fetal_frequency$percentage <- (d7m_fetal_frequency$n/sum(d7m_fetal_frequency$n)) *100

#***D14M***
d14m_fetal_all <- subset(fetal_all, fetal_all$condition == "D14m", select = c("predicted.annotation.l1","condition"))
d14m_fetal_frequency <- count(d14m_fetal_all, d14m_fetal_all$predicted.annotation.l1)
sum(d14m_fetal_frequency$n)
d14m_fetal_frequency$percentage <- ""
d14m_fetal_frequency$percentage <- (d14m_fetal_frequency$n/sum(d14m_fetal_frequency$n)) *100

#Renaming columns of every table and adding coloumn that has a time point
colnames(d00_fetal_frequency)[1] ="predicted.annotation.l1"
d00_fetal_frequency$condition <- "D00"

colnames(d0_fetal_frequency)[1] ="predicted.annotation.l1"
d0_fetal_frequency$condition <- "D0"

colnames(d7m_fetal_frequency)[1] ="predicted.annotation.l1"
d7m_fetal_frequency$condition <- "D7m"

colnames(d14m_fetal_frequency)[1] ="predicted.annotation.l1"
d14m_fetal_frequency$condition <- "D14m"

colnames(d7c_fetal_frequency)[1] ="predicted.annotation.l1"
d7c_fetal_frequency$condition <- "D7c"

colnames(d14c_fetal_frequency)[1] ="predicted.annotation.l1"
d14c_fetal_frequency$condition <- "D14c"

total_fetal_freq <- rbind(d00_fetal_frequency, d0_fetal_frequency,d7c_fetal_frequency,d14c_fetal_frequency,d7m_fetal_frequency,d14m_fetal_frequency)

#Putting columns in a specific order
total_fetal_freq$condition <- factor(total_fetal_freq$condition, levels = c("D00", "D0","D7m","D14m","D7c","D14c"))

ggplot(data =  total_fetal_freq, aes(x = condition, y = predicted.annotation.l1)) + 
  geom_tile(aes(fill = percentage)) + scale_fill_gradient2(high="blue", guide="colorbar",aesthetics="fill") 

```

Workflow for inputting azimuth table for human adipocyte cells. The outputted heatmap is representing the number of cells assigned to a given cell type. 
```{r}
#ADIPCOYTES W/ ALL DATA 

library(ggplot2)

adipocytes_all<- read.csv(file = "/project2/gilad/emaan/time_project/data/azimuth_adipocyte.tsv", head=TRUE, sep="\t")

#Making a table from the Seruat object including only the meta data
seurat_table_A <- seurat_chondro@meta.data

#In the seurat table making the CMO sequence a column instead of a row
library(tibble)
seurat_table_A <- tibble::rownames_to_column(seurat_table_A, "cell")

adipocyte_all_final <- merge(seurat_table_A, adipocytes_all, by='cell', all.x=TRUE)

#Remove all rows with NA
adipocyte_all_final <- adipocyte_all_final[complete.cases(adipocyte_all_final), ]

#Putting columns in a specific order
adipocyte_all_final$condition <- factor(adipocyte_all_final$condition, levels = c("D00", "D0","D7m","D14m","D7c","D14c"))

#Making heatmap with filling by mapping score
ggplot(data =  adipocyte_all_final, aes(x = condition, y = predicted.celltype.l1)) + 
  geom_tile(aes(fill = mapping.score)) + scale_fill_gradient2(high="blue", guide="colorbar",aesthetics="fill") +
  theme(axis.text.x = element_text(color = "black"),
        axis.text.y = element_text(color = "black"),
        axis.ticks = element_line(color = "black"))

```

Workflow for creating a heatmap that has the frequency of cell in a given condition for a given cell type in the human adipocyte referance. 
```{r}
#ADIPCOYTES W/ ALL DATA FREQEUNCY

#Subseting the fetal all dataframe into dataframes for each time point so we can find the frequencies for cells within each time point

library(dplyr)

#***D00***
d00_adipocyte_all <- subset(adipocyte_all_final, adipocyte_all_final$condition == "D00", select = c("predicted.celltype.l1","condition"))
d00_adipocyte_frequency <- count(d00_adipocyte_all, d00_adipocyte_all$predicted.celltype.l1)
sum(d00_adipocyte_frequency$n)
d00_adipocyte_frequency$percentage <- (d00_adipocyte_frequency$n/sum(d00_adipocyte_frequency$n)) *100

#***D0***
d0_adipocyte_all <- subset(adipocyte_all_final, adipocyte_all_final$condition == "D0", select = c("predicted.celltype.l1","condition"))
d0_adipocyte_frequency <- count(d0_adipocyte_all, d0_adipocyte_all$predicted.celltype.l1)
sum(d0_adipocyte_frequency$n)
d0_adipocyte_frequency$percentage <- (d0_adipocyte_frequency$n/sum(d0_adipocyte_frequency$n)) *100

#***D7C***
d7c_adipocyte_all <- subset(adipocyte_all_final, adipocyte_all_final$condition == "D7c", select = c("predicted.celltype.l1","condition"))
d7c_adipocyte_frequency <- count(d7c_adipocyte_all, d7c_adipocyte_all$predicted.celltype.l1)
sum(d7c_adipocyte_frequency$n)
d7c_adipocyte_frequency$percentage <- (d7c_adipocyte_frequency$n/sum(d7c_adipocyte_frequency$n)) *100

#***D14C***
d14c_adipocyte_all <- subset(adipocyte_all_final, adipocyte_all_final$condition == "D14c", select = c("predicted.celltype.l1","condition"))
d14c_adipocyte_frequency <- count(d14c_adipocyte_all, d14c_adipocyte_all$predicted.celltype.l1)
sum(d14c_adipocyte_frequency$n)
d14c_adipocyte_frequency$percentage <- (d14c_adipocyte_frequency$n/sum(d14c_adipocyte_frequency$n)) *100

#***D7M***
d7m_adipocyte_all <- subset(adipocyte_all_final, adipocyte_all_final$condition == "D7m", select = c("predicted.celltype.l1","condition"))
d7m_adipocyte_frequency <- count(d7m_adipocyte_all, d7m_adipocyte_all$predicted.celltype.l1)
d7m_adipocyte_frequency$percentage <- (d7m_adipocyte_frequency$n/sum(d7m_adipocyte_frequency$n)) *100

#***D14M***
d14m_adipocyte_all <- subset(adipocyte_all_final, adipocyte_all_final$condition == "D14m", select = c("predicted.celltype.l1","condition"))
d14m_adipocyte_frequency <- count(d14m_adipocyte_all, d14m_adipocyte_all$predicted.celltype.l1)
d14m_adipocyte_frequency$percentage <- (d14m_adipocyte_frequency$n/sum(d14m_adipocyte_frequency$n)) *100

#Renaming columns of every table and adding coloumn that has a time point
colnames(d00_adipocyte_frequency)[1] ="predicted.annotation.l1"
d00_adipocyte_frequency$condition <- "D00"

colnames(d0_adipocyte_frequency)[1] ="predicted.annotation.l1"
d0_adipocyte_frequency$condition <- "D0"

colnames(d7m_adipocyte_frequency)[1] ="predicted.annotation.l1"
d7m_adipocyte_frequency$condition <- "D7m"

colnames(d14m_adipocyte_frequency)[1] ="predicted.annotation.l1"
d14m_adipocyte_frequency$condition <- "D14m"

colnames(d7c_adipocyte_frequency)[1] ="predicted.annotation.l1"
d7c_adipocyte_frequency$condition <- "D7c"

colnames(d14c_adipocyte_frequency)[1] ="predicted.annotation.l1"
d14c_adipocyte_frequency$condition <- "D14c"

total_adipocyte_freq <- rbind(d00_adipocyte_frequency, d0_adipocyte_frequency,d7c_adipocyte_frequency,d14c_adipocyte_frequency)

#Putting columns in a specific order
total_adipocyte_freq$condition <- factor(total_adipocyte_freq$condition, levels = c("D00", "D0","D7c","D14c"))

ggplot(data =  total_adipocyte_freq, aes(x = condition, y = predicted.annotation.l1)) + 
  geom_tile(aes(fill = percentage)) + scale_fill_gradient2(high="blue", guide="colorbar",aesthetics="fill") +
  theme(axis.text.x = element_text(color = "black"),
        axis.text.y = element_text(color = "black"),
        axis.ticks = element_line(color = "black"))
```

Workflow for inputting azimuth table for human heart cells. The outputted heatmap is representing the number of cells assigned to a given cell type. 
```{r}
#HEART W/ ALL DATA 

library(ggplot2)

heart_all<- read.csv(file = "/project2/gilad/emaan/time_project/data/azimuth_heart.tsv", head=TRUE, sep="\t")

#Making a table from the Seruat object including only the meta data
seurat_table_H <- seurat_chondro@meta.data

#In the seurat table making the CMO sequence a column instead of a row
library(tibble)
seurat_table_H <- tibble::rownames_to_column(seurat_table_H, "cell")

heart_all_final <- merge(seurat_table_H, heart_all, by='cell', all.x=TRUE)

#Remove all rows with NA
heart_all_final <- heart_all_final[complete.cases(heart_all_final), ]

#Putting columns in a specific order
heart_all_final$condition <- factor(heart_all_final$condition, levels = c("D00", "D0","D7m","D14m","D7c","D14c"))

#Making heatmap with filling by mapping score
ggplot(data =  heart_all_final, aes(x = condition, y = predicted.celltype.l2)) + 
  geom_tile(aes(fill = mapping.score)) + scale_fill_gradient2(high="blue", guide="colorbar",aesthetics="fill") +
  theme(axis.text.x = element_text(color = "black"),
        axis.text.y = element_text(color = "black"),
        axis.ticks = element_line(color = "black")) 

```

Workflow for creating a heatmap that has the frequency of cell in a given condition for a given cell type in the human adipocyte referance. 
```{r}
#HEART W/ ALL DATA FREQEUNCY

library(dplyr)

#***D00***
d00_heart_all <- subset(heart_all_final, heart_all_final$condition == "D00", select = c("predicted.celltype.l2","condition"))
d00_heart_frequency <- count(d00_heart_all, d00_heart_all$predicted.celltype.l2)
d00_heart_frequency$percentage <- (d00_heart_frequency$n/sum(d00_heart_frequency$n)) *100

#***D0***
d0_heart_all <- subset(heart_all_final, heart_all_final$condition == "D0", select = c("predicted.celltype.l2","condition"))
d0_heart_frequency <- count(d0_heart_all, d0_heart_all$predicted.celltype.l2)
d0_heart_frequency$percentage <- (d0_heart_frequency$n/sum(d0_heart_frequency$n)) *100

#***D7C***
d7c_heart_all <- subset(heart_all_final, heart_all_final$condition == "D7c", select = c("predicted.celltype.l2","condition"))
d7c_heart_frequency <- count(d7c_heart_all, d7c_heart_all$predicted.celltype.l2)
d7c_heart_frequency$percentage <- (d7c_heart_frequency$n/sum(d7c_heart_frequency$n)) *100

#***D14C***
d14c_heart_all <- subset(heart_all_final, heart_all_final$condition == "D14c", select = c("predicted.celltype.l2","condition"))
d14c_heart_frequency <- count(d14c_heart_all, d14c_heart_all$predicted.celltype.l2)
d14c_heart_frequency$percentage <- (d14c_heart_frequency$n/sum(d14c_heart_frequency$n)) *100

#***D7M***
d7m_heart_all <- subset(heart_all_final, heart_all_final$condition == "D7m", select = c("predicted.celltype.l2","condition"))
d7m_heart_frequency <- count(d7m_heart_all, d7m_heart_all$predicted.celltype.l2)
d7m_heart_frequency$percentage <- (d7m_heart_frequency$n/sum(d7m_heart_frequency$n)) *100

#***D14M***
d14m_heart_all <- subset(heart_all_final, heart_all_final$condition == "D14m", select = c("predicted.celltype.l2","condition"))
d14m_heart_frequency <- count(d14m_heart_all, d14m_heart_all$predicted.celltype.l2)
d14m_heart_frequency$percentage <- (d14m_heart_frequency$n/sum(d14m_heart_frequency$n)) *100

#Renaming columns of every table and adding coloumn that has a time point
colnames(d00_heart_frequency)[1] ="predicted.annotation.l2"
d00_heart_frequency$condition <- "D00"

colnames(d0_heart_frequency)[1] ="predicted.annotation.l2"
d0_heart_frequency$condition <- "D0"

colnames(d7m_heart_frequency)[1] ="predicted.annotation.l2"
d7m_heart_frequency$condition <- "D7m"

colnames(d14m_heart_frequency)[1] ="predicted.annotation.l2"
d14m_heart_frequency$condition <- "D14m"

colnames(d7c_heart_frequency)[1] ="predicted.annotation.l2"
d7c_heart_frequency$condition <- "D7c"

colnames(d14c_heart_frequency)[1] ="predicted.annotation.l2"
d14c_heart_frequency$condition <- "D14c"

total_heart_freq <- rbind(d00_heart_frequency, d0_heart_frequency,d7c_heart_frequency,d14c_heart_frequency)

#Putting columns in a specific order
total_heart_freq$condition <- factor(total_heart_freq$condition, levels = c("D00", "D0","D7c","D14c"))

ggplot(data =  total_heart_freq, aes(x = condition, y = predicted.annotation.l2)) + 
  geom_tile(aes(fill = percentage)) + scale_fill_gradient2(high="blue", guide="colorbar",aesthetics="fill") +
  theme(axis.text.x = element_text(color = "black"),
        axis.text.y = element_text(color = "black"),
        axis.ticks = element_line(color = "black")) 
```

Making histograms: (1) for a given cell type the range of cells within a timepoint are compared (2) for a given timepoint the range of cells within different cell types are compared
```{r}

#***Fetal Histograms***

fetal_vascular <- subset(fetal_all, fetal_all$predicted.annotation.l1 == "Vascular endothelial cells", select=c("mapping.score","condition","predicted.annotation.l1"))

fetal_stromal <- subset(fetal_all, fetal_all$predicted.annotation.l1 == "Stromal cells", select=c("mapping.score","condition","predicted.annotation.l1"))

fetal_smooth <- subset(fetal_all, fetal_all$predicted.annotation.l1 == "Smooth muscle cells", select=c("mapping.score","condition","predicted.annotation.l1"))

fetal_PAEP <- subset(fetal_all, fetal_all$predicted.annotation.l1 == "PAEP_MECOM positive cells", select=c("mapping.score","condition","predicted.annotation.l1"))

fetal_CCL19 <- subset(fetal_all, fetal_all$predicted.annotation.l1 == "CCL19_CCL21 positive cells", select=c("mapping.score","condition","predicted.annotation.l1"))

fetal_IGFBP1_DKK1 <- subset(fetal_all, fetal_all$predicted.annotation.l1 == "IGFBP1_DKK1 positive cells", select=c("mapping.score","condition","predicted.annotation.l1"))

fetal_epicardial <- subset(fetal_all, fetal_all$predicted.annotation.l1 == "Epicardial fat cells", select=c("mapping.score","condition","predicted.annotation.l1"))

fetal_neuroendocrine <- subset(fetal_all, fetal_all$predicted.annotation.l1 == "Neuroendocrine cells", select=c("mapping.score","condition","predicted.annotation.l1"))
                         
total_subset_fetal<- rbind(fetal_vascular,fetal_stromal,fetal_smooth,fetal_PAEP,fetal_CCL19,fetal_IGFBP1_DKK1,fetal_epicardial,fetal_neuroendocrine)

ggplot(total_subset_fetal, aes(x=predicted.annotation.l1, y=mapping.score, fill=condition)) + 
    geom_boxplot() +
  facet_wrap(~predicted.annotation.l1, scale="free")+
  labs(x="Cell Assignment", y="Mapping Score")+
   theme_classic()

ggplot(total_subset_fetal, aes(x=predicted.annotation.l1, y=mapping.score, fill=predicted.annotation.l1)) + 
    geom_boxplot() +
  facet_wrap(~condition, scale="free")+
  labs(x="Cell Assignment", y="Mapping Score")+
   theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
  
#***Adipocyte Histograms***

adipocyte_macrophage <- subset(adipocyte_all_final, adipocyte_all_final$predicted.celltype.l1 == "Macrophage", select=c("mapping.score","condition","predicted.celltype.l1"))

adipocyte_endothelial <- subset(adipocyte_all_final, adipocyte_all_final$predicted.celltype.l1 == "Endothelial", select=c("mapping.score","condition","predicted.celltype.l1"))

adipocyte_ASPC <- subset(adipocyte_all_final, adipocyte_all_final$predicted.celltype.l1 == "ASPC", select=c("mapping.score","condition","predicted.celltype.l1"))

adipocytes_smooth <- subset(adipocyte_all_final, adipocyte_all_final$predicted.celltype.l1 == "Smooth Muscle", select=c("mapping.score","condition","predicted.celltype.l1"))

                         
total_subset_adipocyte<- rbind(adipocyte_macrophage,adipocyte_endothelial,adipocyte_ASPC,adipocytes_smooth)

ggplot(total_subset_adipocyte, aes(x=predicted.celltype.l1, y=mapping.score, fill=condition)) + 
    geom_boxplot() +
  facet_wrap(~predicted.celltype.l1, scale="free")+
  labs(x="Cell Assignment", y="Mapping Score")+
   theme_classic()


ggplot(total_subset_adipocyte, aes(x=predicted.celltype.l1, y=mapping.score, fill=predicted.celltype.l1)) + 
    geom_boxplot() +
  facet_wrap(~condition, scale="free")+
  labs(x="Cell Assignment", y="Mapping Score")+
   theme_classic()

#***Heart Histograms***
heart_mesothelial <- subset(heart_all_final, heart_all_final$predicted.celltype.l2 == "Mesothelial", select=c("mapping.score","condition","predicted.celltype.l2"))

heart_pericyte <- subset(heart_all_final, heart_all_final$predicted.celltype.l2 == "Pericyte", select=c("mapping.score","condition","predicted.celltype.l2"))

heart_fibroblast <- subset(heart_all_final, heart_all_final$predicted.celltype.l2 == "Fibroblast", select=c("mapping.score","condition","predicted.celltype.l2"))

                         
total_subset_heart<- rbind(heart_mesothelial,heart_pericyte,heart_fibroblast)

ggplot(total_subset_heart, aes(x=predicted.celltype.l2, y=mapping.score, fill=condition)) + 
    geom_boxplot() +
  facet_wrap(~predicted.celltype.l2, scale="free")+
  labs(x="Cell Assignment", y="Mapping Score")+
   theme_classic()

ggplot(total_subset_heart, aes(x=predicted.celltype.l2, y=mapping.score, fill=predicted.celltype.l2)) + 
    geom_boxplot() +
  facet_wrap(~condition, scale="free")+
  labs(x="Cell Assignment", y="Mapping Score")+
   theme_classic()

```

