---
title: "Mapping_Data"
output: html_document
date: '2024-05-30'
---

Mapping EM+GH to Wu/EB dataset. This involves creating (1) a query data set which is the EM+GH integrated data and (2) a reference data set which is the Wu/EB data. 
```{r}

#Load and preprocess reference dataset
wu_combined_rev <- readRDS("/project/gilad/ghousman/chondro-human-chimp/hc-chondro-time/chondro-time-evo/data/external/wu_combined_rev.rds")

eb_data <- readRDS(file="/project2/gilad/kenneth/share/pilot.humans.rds")
colnames(eb_data@meta.data)[colnames(eb_data@meta.data) == "labels"] <- "ChondroStage"

# Normalize, find variable features, scale data, run PCA, and perform clustering
wu_combined_rev <- NormalizeData(wu_combined_rev)
wu_combined_rev <- FindVariableFeatures(wu_combined_rev, selection.method = "vst", nfeatures = 2000)
wu_combined_rev <- ScaleData(wu_combined_rev, verbose = FALSE)
wu_combined_rev <- RunPCA(wu_combined_rev, npcs = 100, verbose = FALSE)

eb_data  <- NormalizeData(eb_data)
eb_data  <- FindVariableFeatures(eb_data , selection.method = "vst", nfeatures = 2000)
eb_data  <- ScaleData(eb_data , verbose = FALSE)
eb_data  <- RunPCA(eb_data, npcs = 100, verbose = FALSE)

# Elbow plot to determine number of PCs to use (optional step for manual inspection)
ElbowPlot(wu_combined_rev)
DimHeatmap(wu_combined_rev, dims = 1:50, cells = 500, balanced = TRUE)

# Run UMAP and Find Neighbors using the chosen number of PCs.
wu_combined_rev <- RunUMAP(wu_combined_rev, reduction = "pca", dims = 1:70, reduction.name = "wnn.umap", return.model = TRUE)
wu_combined_rev <- FindNeighbors(wu_combined_rev, reduction = "pca", dims = 1:70)

eb_data  <- RunUMAP(eb_data, reduction = "pca", dims = 1:70, reduction.name = "wnn2.umap", return.model = TRUE)
eb_data  <- FindNeighbors(eb_data, reduction = "pca", dims = 1:70)

# Perform clustering
wu_combined_rev <- FindClusters(wu_combined_rev, resolution = 0.5)
eb_data  <- FindClusters(eb_data, resolution = 0.5)

DimPlot(wu_combined_rev, group.by = "ChondroStage")
DimPlot(eb_data, group.by = "labels", label=FALSE)


# Proceed with the integrated object
integrated_ref <- ScaleData(integrated_ref)
integrated_ref <- RunPCA(integrated_ref, npcs = 30)
integrated_ref1 <- RunUMAP(integrated_ref, dims = 1:30, reduction.name="wnn.umap.int", return.model = TRUE)


# Load and preprocess query dataset (make sure the PCs match the reference dataset)
load("/project/gilad/emaan/time_project/data/integrating_EM_GH/cells.combined_integrated_sw.RData")

cells.combined <- RunUMAP(cells.combined, reduction = "pca", dims = 1:50)
cells.combined <- FindNeighbors(cells.combined, reduction = "pca", dims = 1:50)
cells.combined <- FindClusters(cells.combined, resolution = 0.5)
DimPlot(cells.combined, reduction = "umap", group.by = "condition")

reference_features <- VariableFeatures(integrate)
query_features <- VariableFeatures(query)
common_features <- intersect(reference_features, query_features)

# Find anchors between reference and query datasets
anchors <- FindTransferAnchors(
  reference = integrate,
  query = query,
  features = common_features,
  normalization.method = "LogNormalize",
  reference.reduction = "cca",
  dims = 1:30
)

reference <- RunUMAP(reference, reduction = "pca", dims = 1:30, reduction.name = "wnn3.umap")

# Map query data using reference UMAP model
query_chondro2 <- MapQuery(
  anchorset = anchors,
  query = integrate,
  reference = reference,
  refdata = "orig.ident",
  reference.reduction = "pca",
  reduction.model = "wnn3.umap"
)

# Check available reductions in query_chondro2
print(Reductions(query_chondro2))

# Plot using the correct reduction name
if ("ref.umap" %in% Reductions(query_chondro2)) {
  DimPlot(query_chondro2, reduction = "ref.umap", group.by = "predicted.id", label = TRUE, label.size = 3, repel = TRUE)
} else {
  stop("UMAP reduction not found in the query Seurat object.")
}

DimPlot(query_chondro2, reduction = "ref.umap", group.by = "predicted.id", label = TRUE, label.size = 3, repel = TRUE)

```

Plotting predicted.id scores vs. time points. 
```{r}


library(ggplot2)
library(dplyr)

query_df <- query_chondro2@meta.data

query_d0 <- subset(query_df, condition=="D0")
query_d00 <- subset(query_df, condition=="D00")
query_d7m <- subset(query_df, condition=="D7m")
query_d14m <- subset(query_df, condition=="D14m")
query_d7c <- subset(query_df, condition=="D7c")
query_d14c <- subset(query_df, condition=="D14c")

# Ensure 'condition' and 'predicted.id' are factors with specific order
query_df$condition <- factor(query_df$condition, levels = c("d00", "d0", "d7m", "d7", "d14m", "d14"))
query_df$predicted.id <- factor(query_df$predicted.id, levels = c("d7", "d14", "d28", "d42"))

# Bar Plot: Count of cells in each timepoint category for each reference timepoint
bar_plot_data <- query_d14c %>%
  group_by(condition, predicted.id) %>%
  summarise(count = n())

ggplot(bar_plot_data, aes(x = condition, y = count, fill = predicted.id)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(x="",y = "Number of Cells", fill = "Predicted Timepoint") +
  theme_classic() +
  ggtitle("D14m")

# Box Plot: Distribution of percentage scores for each predicted reference timepoint within each actual timepoint category
ggplot(query_d14c, aes(x = condition, y = predicted.id.score, fill = predicted.id)) +
  geom_boxplot() +
  labs(x = "", y = "Percentage Score", fill = "Predicted Timepoint") +
  theme_classic() +
  scale_y_continuous(limits = c(0, 1))
```

OLD CODE: Mapping EM+GH to Wu dataset. This involves creating (1) a query data set which is the EM+GH integrated data and (2) a reference data set which is the Wu data. This was the initial code I used without having the query data set undergo any PCA. 
```{r}

library(Seurat)

load("/project/gilad/emaan/time_project/data/seurat_QC_2024.RData")
load("/project/gilad/emaan/time_project/data/GH_batch1_QC.RData")
load("/project/gilad/emaan/time_project/data/GH_batch2_QC.RData")


NA18856 <- subset(seurat_QC_2024, subset = donor_id == "NA18856")
NA18855 <- subset(seurat_QC_2024, subset = donor_id == "NA18855")
NA19160 <- subset(seurat_QC_2024, subset = donor_id == "NA19160")
H1 <- subset(GH_batch1_QC, subset = donor_ID == "H1")
H2 <- subset(GH_batch1_QC, subset = donor_ID == "H2")
H3 <- subset(GH_batch2_QC, subset = donor_ID == "H3")
H5 <- subset(GH_batch2_QC, subset = donor_ID == "H5")

#Creating a list of the Seurat objects
individual_list <- list(NA18856, NA18855, NA19160, H1,H2,H3,H5)

# normalize and identify variable features for each dataset independently
individual_list <- lapply(X = individual_list, FUN = function(x) {
    x <- NormalizeData(x)
    x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = 2000)
})

#Select features that are repeatedly variable across data sets for integration
features <- SelectIntegrationFeatures(object.list = individual_list)
cell.anchors <- FindIntegrationAnchors(object.list = individual_list, anchor.features = features)

#Creating the integrated data set
cells.combined <- IntegrateData(anchorset = cell.anchors)
DefaultAssay(cells.combined) <- "integrated"
save(cells.combined, file= "/project/gilad/emaan/time_project/data/Wu_reference_mapping/all_cells_combined.RData")

#Pulling Wu data from directory
load("/project/gilad/emaan/time_project/data/wu_combined_rev.RData")

#Mapping Process: query is the chondro data that has been integrated but not undergone pca
anchors <- FindTransferAnchors(
  reference = wu_combined_rev,
  query = cells.combined,
  normalization.method = "LogNormalize",
  reference.reduction = "pca",
  dims = 1:20,
)

wu_combined_20=RunUMAP(wu_combined_rev,return.model=TRUE,reduction.name = "new.UMAP", dims=1:20)

Wu_UMAP_20 <- MapQuery(
  anchorset = anchors,
  query = cells.combined,
  reference = wu_combined_20,
  refdata = wu_combined_20$labels,
  reference.reduction = "pca", 
  reduction.model = "new.UMAP",
)


anchors <- FindTransferAnchors(
  reference = cells.combined,
  query = wu_combined_rev,
  normalization.method = "LogNormalize",
  reference.reduction = "pca",
  dims = 1:20,
)



```

OLD CODE: Mapping EM+GH to KB dataset. This involves creating (1) a query data set which is the EM+GH integrated data and (2) a reference data set which is the KB data. This was the initial code I used without having the query data set undergo any PCA. 
```{r}

#Pulling Kenneth's data from directory
pilot.humans <- readRDS("/project2/gilad/kenneth/share/pilot.humans.rds")
pilot.humans <- subset(pilot.humans, subset = nFeature_RNA > 200 & nFeature_RNA < 6000 & percent.mt < 5)

#Mapping Process: query is the chondro data that has been subsetted but not undergone pca
anchors <- FindTransferAnchors(
  reference = pilot.humans,
  query = cells.combined,
  normalization.method = "LogNormalize",
  reference.reduction = "pca",
  dims = 1:50,
)

pilot.humans_50=RunUMAP(pilot.humans,return.model=TRUE,reduction.name = "new.UMAP", dims=1:50)
save (pilot.humans_50, file= "/project2/gilad/emaan/time_project/data/pilot.humans_50.RData")

KB_UMAP <- MapQuery(
  anchorset = anchors,
  query = cells.combined,
  reference = pilot.humans_50,
  refdata = pilot.humans_50$labels,
  reference.reduction = "pca", 
  reduction.model = "new.UMAP",
)

save(KB_UMAP, file = "/project2/gilad/emaan/time_project/data/KB_UMAP.RData")

p2 = DimPlot(KB_UMAP, reduction = "ref.umap", group.by = "predicted.id", label = TRUE, label.size =3, repel = TRUE)  +xlim(-12,10) +ylim(-10,10) + NoLegend()

p1 = DimPlot(pilot.humans_50, reduction = "new.UMAP", group.by = "labels", label = TRUE, label.size = 3, repel = TRUE) +xlim(-12,10) +ylim(-10,10) + NoLegend()

p1+p2

KB_UMAP_table <- KB_UMAP@meta.data

result <- KB_UMAP_table %>%
  group_by(condition, predicted.id) %>%
  summarize(count = n()) %>%
  arrange(condition, predicted.id)

# Print the result
print(result)
```


Integrating KB data with GH+EM human data (GH's original code shown). The code that I used to process my data is in /project/gilad/emaan/time_project/code/mapping_KB_GHcode.sh. The output files are saved in /project/gilad/emaan/time_project/data/integrating_KB/integrate_KB_var_cca_reg.RData. 
```{r}

#define parameters for integrated data

#filter <- ""
#filter <- ".filterL"
filter <- ".filterC"

set <- "chond-ind"  #all chondrogenic cells

genes <- "Var"  #features that are repeatedly variable across datasets for integration
#genes <- "No0"  #all genes that have at least 1 UMI count across samples
#genes <- "19k"  #all 19397 genes

dimred <- "cca"
#dimred <- "pca"
#dimred <- "ref"

kweigh <- 50
#kweigh <- 100

regout <- "reg" #this takes a long time when genes=No0
#regout <- "non"

#Integrate cells (across individuals)
organoid_data <- readRDS(paste0("./data/06_data",filter,".log.",set,".rds"))
eb_data <- readRDS(file="/project2/gilad/kenneth/share/pilot.humans.rds")

#isolate just human data
organoid_data_human <- append(organoid_data[[1]],append(organoid_data[[3]],append(organoid_data[[5]],organoid_data[[7]])))

#add chondro-stage metadata
eb_data$ChondroStage <- "KB: iPSC-EB"

obj <- append(organoid_data_human,eb_data)
rm(organoid_data,organoid_data_human,eb_data)

#select genes to use for finding integration anchors
if (genes=="Var") {
  obj.features <- SelectIntegrationFeatures(object.list = obj)
  length(obj.features)
}
if (genes=="No0") {
  geneList <- c()
  for(object in obj) {
    geneList <- c(geneList,rownames(object@assays$RNA@counts)[rowSums(object@assays$RNA@counts)!=0])
  }
  obj.features <- unique(geneList)
  length(obj.features)
}
if (genes=="19k") {
  obj.features <- rownames(obj[[1]]@assays$RNA@counts)
  length(obj.features)
}

#scale data and run pca
obj <- lapply(X=obj, FUN=function(x) {
  x <- ScaleData(x, features=obj.features, verbose=FALSE)
  x <- RunPCA(x, features=obj.features, verbose=FALSE)
})

#find integration anchors
if (dimred=="cca") {
  obj.anchors <- FindIntegrationAnchors(object.list=obj,
                                        normalization.method="LogNormalize",
                                        anchor.features=obj.features,
                                        reduction="cca")
}
if (dimred=="pca") {
  obj.anchors <- FindIntegrationAnchors(object.list=obj,
                                        normalization.method="LogNormalize",
                                        anchor.features=obj.features,
                                        reduction="rpca")
}
if (dimred=="ref") {
  ref.data <- c(2,9) #H1-r2 and C1-r2 differentiated best
  obj.anchors <- FindIntegrationAnchors(object.list=obj,
                                        normalization.method="LogNormalize",
                                        anchor.features=obj.features,
                                        reference=ref.data,
                                        reduction="rpca")
}

#integrate data
integrate <- IntegrateData(anchorset=obj.anchors,
                           normalization.method="LogNormalize",
                           k.weight=kweigh)

#regress out unwanted variables
if (regout=="reg") {
  integrate <- ScaleData(integrate, vars.to.regress=c("nCount_RNA","percent.mt"))
}
if (regout=="non") {
  integrate <- ScaleData(integrate, vars.to.regress=NULL, verbose=FALSE)
}

#run pca
integrate <- RunPCA(object=integrate,
                    npcs=100,
                    verbose=FALSE)

#keep all dims that explaim more than 0.1% of variance
pva <- integrate@reductions$pca@stdev^2/integrate@reductions$pca@misc$total.variance
ndim <- length(which(pva>=0.001))
print(ndim)

#run umap
integrate <- RunUMAP(integrate,
                     dims=1:ndim)

#save data
saveRDS(integrate, file=paste0("./data/integrated/06_combined-data-eb-human",filter,".log.",set,".int.",genes,".",dimred,".",kweigh,".",regout,".rds"))

#clear variables
rm(genes,dimred,kweigh,regout)
rm(obj,obj.features,obj.anchors,integrate,pva,ndim)

#visualize data
integrate <- readRDS(file=paste0("./data/integrated/06_combined-data-eb-human",filter,".log.",set,".int.",genes,".",dimred,".",kweigh,".",regout,".rds"))
DimPlot(integrate,
        group.by="ChondroStage",
        reduction="umap") +
  labs(x="UMAP1",y="UMAP2")
DimPlot(integrate,
        group.by="labels",
        label=TRUE,
        reduction="umap") +
  labs(x="UMAP1",y="UMAP2") +
  NoLegend()

```

Visualizing the data. The output file from GH code is stored in /project/gilad/emaan/time_project/data/integrating_KB/integrate_KB_var_cca_reg.RData. 
```{r}
#visualize data EM code
DimPlot(integrate,
        group.by="condition",
        label=TRUE,
        label.size=2,
        reduction="umap") +
  labs(x="UMAP1",y="UMAP2") +
  NoLegend()

# UMAP plot without labels
umap_plot <- DimPlot(integrate, group.by = "condition", reduction = "umap", label=FALSE, label.size=5) +
  labs(x = "UMAP1", y = "UMAP2") +
  NoLegend()

# Specify the clusters you want to label
clusters_to_label <- c("Early Mesoderm 1", "Cardiomyocytes","Epicardial fat cells","Early Ectoderm 1", "Early Endoderm 1") 

# Add labels to the specified clusters
umap_plot_labeled <- LabelClusters(plot = umap_plot, id = "labels", clusters = clusters_to_label, repel = TRUE, size = 3)

# Display the plot
print(umap_plot_labeled)
```

Integrating KB+EM+GH data using my original integration code. This utilizes standard integration with 15 PCs. The output is saved in project/gilad/emaan/time_project/data/integrating_KB/cells.combined_all_KB.RData. 
```{r}

library(Seurat)

load("/project/gilad/emaan/time_project/data/seurat_QC_2024.RData")
load("/project/gilad/emaan/time_project/data/GH_batch1_QC.RData")
load("/project/gilad/emaan/time_project/data/GH_batch2_QC.RData")
load("/project/gilad/emaan/time_project/code/pilot.humans.RData")
pilot.humans <- subset(pilot.humans, subset = nFeature_RNA > 200 & nFeature_RNA < 6000 & percent.mt < 5)


NA18856 <- subset(seurat_QC_2024, subset = donor_id == 'NA18856')
NA18855 <- subset(seurat_QC_2024, subset = donor_id == 'NA18855')
NA19160 <- subset(seurat_QC_2024, subset = donor_id == 'NA19160')
H1 <- subset(GH_batch1_QC, subset = donor_ID == 'H1')
H2 <- subset(GH_batch1_QC, subset = donor_ID == 'H2')
H3 <- subset(GH_batch2_QC, subset = donor_ID == 'H3')
H5 <- subset(GH_batch2_QC, subset = donor_ID == 'H5')

#Creating a list of the Seurat objects
individual_list <- list(NA18856, NA18855, NA19160, H1,H2,H3,H5,pilot.humans)

# normalize and identify variable features for each dataset independently
individual_list <- lapply(X = individual_list, FUN = function(x) {
    x <- NormalizeData(x)
    x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = 2000)
})

#Select features that are repeatedly variable across data sets for integration
features <- SelectIntegrationFeatures(object.list = individual_list)
cell.anchors <- FindIntegrationAnchors(object.list = individual_list, anchor.features = features)

#Creating the integrated data set
cells.combined <- IntegrateData(anchorset = cell.anchors)
DefaultAssay(cells.combined) <- "integrated"

#Standard workflow for visualization and clustering 
cells.combined <- ScaleData(cells.combined, verbose = FALSE)
cells.combined <- RunPCA(cells.combined, npcs = 50, verbose = FALSE)
save(cells.combined, file = "/project/gilad/emaan/time_project/data/cells.combined_all_KB.RData")

#Trying to find how many PCs to include
ElbowPlot(cells.combined)
DimHeatmap(cells.combined, dims = 1:50, cells = 500, balanced = TRUE)
#Try 15, 20, and 50 PCs

cells.combined <- RunUMAP(cells.combined, reduction = "pca", dims = 1:15)
cells.combined <- FindNeighbors(cells.combined, reduction = "pca", dims = 1:15)
cells.combined <- FindClusters(cells.combined, resolution = 0.5)

# Visualization
p1<- DimPlot(cells.combined, reduction = "umap", group.by = "orig.ident")
p2<- DimPlot(cells.combined, reduction = "umap", label = TRUE, repel = TRUE)

```

Integrating Wu data with GH+EM human data (GH's original code shown). The code that I used to process my data is in /project/gilad/emaan/time_project/code/mapping_Wu_GHcode.sh. readRDS("/project/gilad/ghousman/chondro-human-chimp/hc-chondro-time/chondro-time-evo/data/external/wu_combined_rev.rds"). The file is saved in /project/gilad/emaan/time_project/data/Wu_reference_mapping. 
```{r}

#define parameters for integrated data

#filter <- ""
#filter <- ".filterL"
filter <- ".filterC"

set <- "chond-ind"  #all chondrogenic cells

genes <- "Var"  #features that are repeatedly variable across datasets for integration
#genes <- "No0"  #all genes that have at least 1 UMI count across samples
#genes <- "19k"  #all 19397 genes

dimred <- "cca"
#dimred <- "pca"
#dimred <- "ref"

kweigh <- 50
#kweigh <- 100

regout <- "reg" #this takes a long time when genes=No0
#regout <- "non"


#Integrate all cells (across individuals)

organoid_data <- readRDS(paste0("./data/06_data",filter,".log.",set,".rds"))
wu_data  <- readRDS(file="./data/external/wu_combined_rev.rds")
#wu_data <- wu_combined_rev

obj <- append(organoid_data,wu_data)
rm(organoid_data,wu_data)

#select genes to use for finding integration anchors
if (genes=="Var") {
  obj.features <- SelectIntegrationFeatures(object.list = obj)
  length(obj.features)
}
if (genes=="No0") {
  geneList <- c()
  for(object in obj) {
    geneList <- c(geneList,rownames(object@assays$RNA@counts)[rowSums(object@assays$RNA@counts)!=0])
  }
  obj.features <- unique(geneList)
  length(obj.features)
}
if (genes=="19k") {
  obj.features <- rownames(obj[[1]]@assays$RNA@counts)
  length(obj.features)
}

#scale data and run pca
obj <- lapply(X=obj, FUN=function(x) {
  x <- ScaleData(x, features=obj.features, verbose=FALSE)
  x <- RunPCA(x, features=obj.features, verbose=FALSE)
})

#find integration anchors
if (dimred=="cca") {
  obj.anchors <- FindIntegrationAnchors(object.list=obj,
                                        normalization.method="LogNormalize",
                                        anchor.features=obj.features,
                                        reduction="cca")
}
if (dimred=="pca") {
  obj.anchors <- FindIntegrationAnchors(object.list=obj,
                                        normalization.method="LogNormalize",
                                        anchor.features=obj.features,
                                        reduction="rpca")
}
if (dimred=="ref") {
  ref.data <- c(2,9) #H1-r2 and C1-r2 differentiated best
  obj.anchors <- FindIntegrationAnchors(object.list=obj,
                                        normalization.method="LogNormalize",
                                        anchor.features=obj.features,
                                        reference=ref.data,
                                        reduction="rpca")
}

#integrate data
integrate <- IntegrateData(anchorset=obj.anchors,
                           normalization.method="LogNormalize",
                           k.weight=kweigh)

#regress out unwanted variables
if (regout=="reg") {
  integrate <- ScaleData(integrate, vars.to.regress=c("nCount_RNA","percent.mt"))
}
if (regout=="non") {
  integrate <- ScaleData(integrate, vars.to.regress=NULL, verbose=FALSE)
}

#run pca
integrate <- RunPCA(object=integrate,
                    npcs=100,
                    verbose=FALSE)

#keep all dims that explaim more than 0.1% of variance
pva <- integrate@reductions$pca@stdev^2/integrate@reductions$pca@misc$total.variance
ndim <- length(which(pva>=0.001))
print(ndim)

#run umap
integrate <- RunUMAP(integrate,
                     dims=1:ndim)

#save data
saveRDS(integrate, file=paste0("./data/integrated/06_combined-data-wu",filter,".log.",set,".int.",genes,".",dimred,".",kweigh,".",regout,".rds"))

#clear variables
rm(genes,dimred,kweigh,regout)
rm(obj,obj.features,obj.anchors,integrate,pva,ndim)


#visualize data
integrate <- readRDS(file=paste0("./data/integrated/06_combined-data-wu",filter,".log.",set,".int.",genes,".",dimred,".",kweigh,".",regout,".rds"))

DimPlot(integrate,
        group.by="condition",
        reduction="umap") +
  labs(x="UMAP1",y="UMAP2")

FeaturePlot(object = integrate, features = 'nCount_RNA')
```







